Appendix 4: example of index standardization of fishery-independent survey data with inlabru

### 2021-12-11 doc/appendix-pcod-inlabru.Rmd
start adding detail to inlabru example

This model is an extension of the same vignette using sdmTMB.

```{r mesh, echo = TRUE, cache=FALSE}
mesh <- make_mesh(pcod, xy_cols = c("X", "Y"), cutoff = 10)

spde <- inla.spde2.pcmatern(
  mesh = mesh$mesh,
  prior.range = c(10, 0.05), # P(range < 10) = 0.05
  prior.sigma = c(2, 0.05)
) # P(sigma > 2) = 0.05
```

```{r plot-mesh, fig.asp=0.9, out.width="4in"}
plot(mesh)
```

>>>>

This model will attempt to replicate the model fit in Appendix 1 as an example of how index standardization can also be achieved with inlabru.
We will start by building an identical mesh using INLA.
These same functions that are used internally in the sdmTMB `make_mesh()` function.

```{r mesh, echo = TRUE, cache=FALSE}
loc_xy <- as.matrix(pcod[, c("X", "Y"), drop = FALSE])
inla_mesh <- INLA::inla.mesh.create(loc_xy, refine = TRUE, cutoff = 10)

spde <- inla.spde2.pcmatern(
  mesh = mesh$mesh,
  prior.range = c(10, 0.05), # P(range < 10) = 0.05
  prior.sigma = c(2, 0.05) # P(sigma > 2) = 0.05
) 
```

```{r plot-mesh, fig.asp=0.9, out.width="4in"}
plot(spde$mesh)
```

```{r mesh-sdmTMB, echo = TRUE, cache=FALSE}
mesh <- make_mesh(pcod, xy_cols = c("X", "Y"), cutoff = 10)
```
